The \project{unRAVE} catalog

### 2016-08-23 article/unrave.tex
Some words about K2/EPIC mis-classifications

\IfFileExists{vc.tex}{\input{vc.tex}}{\newcommand{\githash}{UNKNOWN}}

@@

Assembling a training set for the main-sequence and sub-giant branch was more complex.
% training set from K2/EPIC?!!
% Identifying obviously bad stars that have been mis-classified by K2/EPIC

@@

% TODO: Replace ZENODO-URL with a data url
Source code for this project is available at \texttt{\url{https://www.github.com/AnnieJumpCannon/RAVE}}.  
This document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels and covariance matrices are available electronically with 
associated metadata at \texttt{\url{ZENODO-URL}} \citep{DATA_REPOSITORY}.  
Please note that it is a condition of using these results that the fifth \rave\ 
data release by \citet{Kunder_2016} must (also) be cited, as the work presented 
here would not have been possible without the tireless efforts of the entire 
\rave\ collaboration, past and present.

@@

@@

>>>>

\IfFileExists{vc.tex}{\input{vc.tex}}{\newcommand{\githash}{UNKNOWN}\newcommand{\giturl}{UNKNOWN}}

@@

Assembling a training set for the main-sequence and sub-giant branch was more complex.
There are no spectroscopic studies that have a large enough overlap with \rave, and
also cover our required range of stellar parameters (e.g., FGKM-type stars).  Moreover,
most of the spectroscopic studies we considered exhibit a flat lower main-sequence, a
consequence of violating the assumption of local thermal equilibrium 
\citep[e.g., see][for a discussion]{Bensby_2014}.  For these reasons we chose to make
use of the \epic\ catalog \citep{Huber_2016} for the training set labels.  The \epic\
catalog follows from the successful \project{Kepler} input catalog \citep{Brown_2011},
and provides probabilistic stellar classifications for $\gtrsim180{,}000$ stars in 
the \project{K2} fields based on the astrometric, photometric, and spectroscopic
information available.  There are 4,611 stars that overlap between \epic\ and \rave.

When the \epic\ posteriors are narrow (i.e., the uncertainties on labels are small),
\citet{Huber_2016} show that the labels are accurate and trustworthy.  However,
\epic\ differs from the \project{Kepler} input catalog because \epic\ does not
benefit from having narrow-band $DDO_{51}$ photometry in order to aid dwarf/giant
classification.  For this reason there are a number of stars that are mis-classified
in the \epic\ catalog.  \citet{Huber_2016} acknowledges this, noting: the fraction 
of X classified as Y could be as much as Z\%; up to Z2\% of X2 could be marked as Y2, 
and \stub{other things}.  In other words, the \epic\ labels are usually of high 
fidelity, and mis-classifications are clearly detectable if spectra are available.
As we will show, when the mis-classifications can be identified from \rave\ spectra, 
the \epic\ catalog makes a suitable training set for the main-sequence and sub-giant
branch in \rave.

% Identifying obviously bad stars that have been mis-classified by K2/EPIC

@@

% TODO: Replace ZENODO-URL with a data url
Source code for this project is available at \texttt{\giturl}.
This document was compiled from revision hash \texttt{\githash} in that repository.
Inferred labels and covariance matrices are available electronically with 
associated metadata at \texttt{\url{ZENODO-URL}} \citep{DATA_REPOSITORY}.  
Please note that it is a condition of using these results that the fifth \rave\ 
data release by \citet{Kunder_2016} must (also) be cited, as the work presented 
here would not have been possible without the tireless efforts of the entire 
\rave\ collaboration, past and present.

@@

\bibitem[Bensby et al.(2014)]{Bensby_2014} Bensby, T., Feltzing, S., \& Oey, M.~S.\ 2014, \aap, 562, A71

@@

\bibitem[Brown et al.(2011)]{Brown_2011} Brown, T.~M., Latham, D.~W., Everett, M.~E., \& Esquerdo, G.~A.\ 2011, \aj, 142, 112
